\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}

\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

% Adjusted for dot bullet points
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[left=0pt, label={\tiny$\bullet$}, labelsep=1em, itemsep=0mm, noitemsep]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[left=0pt, label={\tiny$\bullet$}, labelsep=1em, itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[left=0pt, label={\tiny$\bullet$}, labelsep=1em, itemsep=0mm, noitemsep]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
% \newcommand{\name}{Prathamesh Pranjale} % Your Name

% \newcommand{\phone}{xxxxxxxxxx} % Your Phone Number
% \newcommand{\emaila}{youremail@email.com} %Email 1
% \newcommand{\emailb}{officialemail@iiitkota.ac.in} %Email 2

% \documentclass[a4paper,11pt]{article}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{geometry}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\pagestyle{empty}
\renewcommand{\labelitemi}{\textbullet} % Use bullet point as dot

% Custom itemize settings
\newlist{myitemize}{itemize}{1}
\setlist[myitemize,1]{left=0pt, label={\textbullet}, labelsep=1em, itemsep=0mm, noitemsep}

\begin{document}
\fontfamily{cmr}\selectfont

%----------HEADING-----------------
\parbox{\dimexpr\linewidth-0.75cm\relax}{
\begin{tabularx}{\linewidth}{L r}
  \textbf{\Large Prathamesh Pranjale} & \raisebox{0.0\height}{\footnotesize \faPhone} +91-7028092060 \\
  \textbf{\Large Software Engineer} & \href{mailto:prathameshpranjale777@gmail.com}{\raisebox{0.0\height}{\footnotesize \faEnvelope}\ prathameshpranjale777@gmail.com} \\
  & \href{https://github.com/prathameshpranjale}{\raisebox{0.0\height}{\footnotesize \faGithub}\ github.com/prathameshpranjale} \\
  & \href{https://www.linkedin.com/in/prathamesh-pranjale-18929b218/}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ linkedin.com/in/prathamesh-pranjale}
\end{tabularx}
}


\vspace{-8mm}

%-----------EDUCATION-----------
\section{\textbf{Education}}
\noindent
\textbf{Pimpri Chinchwad College of Engineering, Pune} \hfill \textit{Graduation Year: 2024} \\
\textit{B.Tech in Electronics and Tele-Communication Engineering} \hfill \textit{CGPA: 8.96} \\
\textit{Minor in Software Engineering} \hfill \textit{CGPA: 8.55} \\
\vspace{-2mm}


%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
\noindent
\textbf{Rudder Analytics Private Limited, Pune} \\
\textit{Associate Analyst} \hspace{9.2cm} \textit{December 18, 2023 – May 17, 2024} \\
\vspace{-3mm}
\begin{itemize}[left=0pt, label={\textbullet}, labelsep=1em, itemsep=0mm, noitemsep]
  \item Optimized database management and query performance with \textbf{MySQL}.
  \item Executed ETL processes using \textbf{Python}, improving data workflow efficiency.
  \item Developed and maintained \textbf{RESTful APIs} in \textbf{Python} for seamless integration.
  \item Designed and deployed interactive dashboards using \textbf{Power BI}.
  \item Implemented data storage, processing, and analytics solutions on \textbf{Google Cloud Platform (GCP)}.
  \item Created actionable data visualizations and reports in \textbf{Tableau} for informed decision-making.
\end{itemize}
\vspace{-6mm}



%-----------PROJECTS-----------------
\section{\textbf{Personal Projects}}
\noindent
\textbf{Image Captioning using Beam Search and Greedy Search} \\
\vspace{-3mm}
\begin{itemize}[left=0pt, label={\textbullet}, labelsep=1em, itemsep=0mm, noitemsep]
  \item Implemented an image captioning model with InceptionV3 and deep learning techniques.
  \item Developed caption prediction models using greedy and beam search algorithms.
  \item Improved caption accuracy and descriptiveness.
  \item \textbf{Tech stack: Python, Numpy, Pandas}
\end{itemize}

\vspace{-2.5mm} % Adjust this value to control space between projects

\noindent
\textbf{Backend Video Hosting Platform} \\
\vspace{-3mm}
\begin{itemize}[left=0pt, label={\textbullet}, labelsep=1em, itemsep=0mm, noitemsep]
  \item Developed a comprehensive backend system with Node.js, Express.js, MongoDB, and Mongoose.
  \item Implemented features like user authentication, video upload, and engagement actions.
  \item Ensured secure authentication and token management.
  \item Gained experience in scalable backend solutions.
  \item \textbf{Tech stack: Node.js, Express.js, MongoDB, Mongoose, JWT, bcrypt}
\end{itemize}

\vspace{-2.5mm} % Adjust this value to control space between projects

\noindent
\textbf{Drone-based Surveillance System for Port Areas} \\
\vspace{-3mm}
\begin{itemize}[left=0pt, label={\textbullet}, labelsep=1em, itemsep=0mm, noitemsep]
  \item Designed a drone-based system to monitor vessels and detect encroachments.
  \item Integrated cameras for real-time streaming and used YOLO for person detection.
  \item Enhanced surveillance with advanced detection algorithms.
  \item \textbf{Tech stack: Python, Ubuntu, YOLO, Jetson Nano, TensorFlow}
\end{itemize}
\vspace{-6mm}

%-----------Technical Skills and Interests-----------------
\section{\textbf{Technical Skills and Interests}}
\begin{description}[left=0pt, labelsep=1em, itemsep=0mm, noitemsep]
    \item[\textbf{Programming Languages:}] C++, Java, Python, JavaScript, Node.js
    \item[\textbf{Developer Tools:}] VS Code, GitHub, Git, Postman
    \item[\textbf{Frameworks and Libraries:}] Express.js, Mongoose, React
    \item[\textbf{Cloud Platforms and Databases:}] Google Cloud Platform (GCP), MongoDB, SQL
    \item[\textbf{Software Development:}] Backend Development, RESTful APIs, JWT, Object-Oriented Programming, \newline Data Structures, Algorithms
    \item[\textbf{Soft Skills:}] Problem Solving, Communication, Team Collaboration
    \item[\textbf{Areas of Interest:}] Software Engineering, Backend Development, Web Development, Machine Learning
\end{description}

\vspace{-7mm}
%-----------Achievements-----------------
\section{\textbf{Achievements}}
\begin{description}[left=0pt, labelsep=1em, itemsep=0mm, noitemsep]
    \item[\textbf{Led Team in Smart India Hackathon:}] Successfully led a team to build a student study portal.
    \item[\textbf{GeeksforGeeks:}] Solved over 500 questions, demonstrating strong problem-solving skills.
    \item[\textbf{LeetCode:}] Achieved a 1480 rating by solving over 200 coding problems.
    \item[\textbf{Certification in Data Structures:}] Demonstrated proficiency in key algorithms.
    \item[\textbf{HackerRank Certifications:}] Earned certifications in Problem Solving and SQL, showcasing advanced problem-solving and database query skills.
\end{description}
\vspace{-7mm}


\end{document}
